### 2021-05-19 README.Rmd
tidy up and add note on how to create the tarball to the README
update renv parts

>>>>

- Note that you need to have the development version of `knitr` and `rmarkdown`
- Packages used described in `renv.lock` file
- you can install the packages used in the lockfile by running:

```r
library(renv)
restore()
```

This will install the packgages used in the lockfile, for this project. It should not impact your other local R installations.
